---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Homework6

<!-- badges: start -->

[![R-CMD-check.yaml](https://github.com/Janakass3m/Homework6/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Janakass3m/Homework6/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

# Homework6: Sparse Numeric Vector Class and Operations

The **Homework6** package implements an S4 class called `sparse_numeric` for efficiently representing and manipulating numeric vectors that contain many zeros. This package includes arithmetic operations, statistical methods, full documentation generated with **roxygen2**, automated testing using **testthat**, and a pkgdown documentation website.

The package includes:

-   Custom S4 class `sparse_numeric`

-   Arithmetic methods (`sparse_add`, `sparse_sub`, `sparse_mult`)

-   Cross-product, Euclidean norm, and mean computations

-   Standardization method that works without converting to dense format

-   Full documentation generated with **roxygen2**

-   Automated testing using **testthat**

-   GitHub Actions continuous integration

-   pkgdown documentation website

This package passes **R CMD check** with *0 errors, 0 warnings, and 0 notes*.

## Installation

You can install the development version of Homework6 like so:

``` r
# install.packages("devtools")
devtools::install_github("JanaKassem/Homework6")
```

## Features

The class stores sparse vectors using:

-   value: numeric vector of non-zero entries

-   pos: positions of these non-zero values

-   length: total length of the full vector

### Implemented Methods

-   `sparse_add(x, y)`

-   `sparse_sub(x, y)`

-   `sparse_mult(x, y)`

-   `sparse_crossprod(x, y)`

-   `mean(x)`

-   `norm(x)`

-   `standardize(x)`

-   `as(x, "numeric")`

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Homework6)
## basic example code
x <- as(c(0, 2, 0, 4), "sparse_numeric")
y <- as(c(1, 0, 3, 0), "sparse_numeric")

# Addition
sparse_add(x, y)

# Mean
mean(x)

# Norm
norm(x)

# Standardize
standardize(x)
```

## pkgdown Website

The pkgdown documentation website will be available at: <https://janakass3m.github.io/Homework6/>

## License

This package is released under the MIT License.\
See the `LICENSE.md` file for details.
